---
title: "Pstat-131-Homework1"
author: "Thomas Shi"
date: "2022/4/4"
output:
  pdf_document: default
  html_document: default
  word_document: default
---
```{r setup, include=FALSE}
# packages
library(tidyverse)
library(faraway)
library(ggplot2)
library(corrplot)
```
Machine Learning Main Ideas

1
In supervised learning there is a supervisor Y which is real data. Y is a raw observed output.
The outcome of our model wants to be as close as possible to Y without overfitting.

In unsupervised learning, we fit our model without a supervisor. There are no responses.
We want to find the pattern of our data without a specific goal. Most of unsupervised learning are
clustering.

The difference between supervised learning and unsupervised learning is whether there is a supervisor
or not.

2
Regression models are used to predict and analyze quantitative data. Data are numerical values and
continuous.

Classification models are used to analyze qualitative data with categorical values.

4
Descriptive models are used to visualize and emphasize a trend in data.

Inferential models are used to detect significant features, test theories, and state relationship or
causation between outcome and predictors

Predictive models are used to predict Y with minimum reducible error and the best combo of features

5, 
Mechanistic means that models are fitted with parameters, while empirically-driven doesn't fit model with
parameters. For mechanistic, it is impossible to fit a perfectly matched function. For empirically-driven,
large numbers of observations are needed. Empirically-driven are more flexible than mechanistic, but 
mechanistic can increase its flexibility by increasing the number of parameters. Both of them will face the risk
of overfitting

I think, mechanistic will be easier to understand because with parameters, the relationship between x and y will
be easier to interpret and be understood

6
The first question is predictive because it asks to predict a probability of a voter that will 
vote in favor of candidate

The second question is inferential because it asks for a relationship between personal contact with 
the candidate and the likelihood of support for the condidate

Exploratory Data Analysis

1
```{r, echo = T}
hwy <- pull(mpg, hwy)
hist(hwy)
```
The histogram of highway miles per gallon is right-skewed

2
```{r, echo = T}
cty <- pull(mpg, cty)
ggplot(data = mpg, mapping = aes(x = hwy, y = cty)) + 
  geom_point()
```
There is a strong positive linear relationship between highway miles per gallon and cty.
It means that if hwy increase cty will increase with it linearly with high probability.

3
```{r, echo = T, fig.height = 15}
manufacturer <- table(mpg$manufacturer)
manufacturer
ggplot(data = mpg, aes(y = manufacturer)) + geom_bar(orientation = "y")

```
Dodge produce the most and Lincoln produce the least

4
```{r, echo = T}
ggplot(data = mpg, aes(x = hwy, group = cty, fill = cty)) + geom_boxplot()
```
Except for some extreme values, when values of cty are relatively high or relatively low the rage of hwy is wider.
When the values of cty are moderate, the rage of hwy are relatively narrower.

5
```{r, echo = T}
mpg_small <- mpg %>% 
  select(displ,year,cyl,cty,hwy,)
mpg_small
M <- cor(mpg_small)
corrplot(M, method = 'square', order = 'FPC', type = 'lower', diag = FALSE)
```
All the categorical variables are removed
There is a positive relationship between hwy and cty, and cyl and displ
There is a negative relationship between displ and cty, cyl and cty, displ and hwy, and cyl and hwy
I am surprise that number of cylinders and engine displacement has a negative relationship with
miles per gallon. Rest of the relationship make sense to me


























